---
title: "tables"
author: "Farah Allouch"
date: "`r format(Sys.time(), ' %B %d, %Y')`"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

rm(list = ls())
options(scipen = 999)

library(tidyverse)
library(gtsummary)
```

\newpage
```{r}
load("C:/Users/fallouch/Box/PhD/CHERISH/CHERISH/deidRaw/output/cherish.RData")

cherish <- cherish %>% 
  select(q6.factor, q7.factor, q8.factor,
         q10.factor, q12.factor, q14.factor, 
         a_asking_questions_to_your.factor, c_understanding_medical_tr.factor,
         a_religious_spiritual_beli.factor, b_i_tend_to_avoid_things_h.factor,
         q28, q29.factor, q33.factor)

cherish <- cherish %>% 
  mutate(q6.factor = case_when(q6.factor == "Yes" ~ 1,
                               q6.factor == "No" ~ 0),
         q7.factor = case_when(q7.factor == "Yes" ~ 1,
                               q7.factor == "No" ~ 0),
         q8.factor = case_when(q8.factor == "Yes" ~ 1,
                               q8.factor == "No" ~ 0),
         q10.factor = case_when(q10.factor == "Yes" ~ 1,
                                q10.factor == "No" ~ 0),
         q12.factor = case_when(q12.factor == "Yes" ~ 1,
                                q12.factor == "No" ~ 0),
         q14.factor = case_when(q14.factor == "Yes" ~ 1,
                                q14.factor == "No" ~ 0),
         a_asking_questions_to_your.factor_numeric = as.numeric(case_when(a_asking_questions_to_your.factor == "Not at All" ~ 1,
                                                               a_asking_questions_to_your.factor == "A Little Bit" ~ 2,
                                                               a_asking_questions_to_your.factor == "Somewhat" ~ 3,
                                                               a_asking_questions_to_your.factor == "Quite a Bit" ~ 4,
                                                               a_asking_questions_to_your.factor == "Extremely" ~ 5)),
         c_understanding_medical_tr.factor_numeric = as.numeric(case_when(c_understanding_medical_tr.factor == "Not at All" ~ 1,
                                                               c_understanding_medical_tr.factor == "A Little Bit" ~ 2,
                                                               c_understanding_medical_tr.factor == "Somewhat" ~ 3,
                                                               c_understanding_medical_tr.factor == "Quite a Bit" ~ 4,
                                                               c_understanding_medical_tr.factor == "Extremely" ~ 5)), 
         a_religious_spiritual_beli.factor_numeric = as.numeric(case_when(a_religious_spiritual_beli.factor == "Strongly Disagree" ~ 1,
                                                               a_religious_spiritual_beli.factor == "Somewhat Disagree" ~ 2,
                                                               a_religious_spiritual_beli.factor == "Neutral" ~ 3,
                                                               a_religious_spiritual_beli.factor == "Somewhat Agree" ~ 4,
                                                               a_religious_spiritual_beli.factor == "Strongly Agree" ~ 5)), 
         b_i_tend_to_avoid_things_h.factor_numeric = as.numeric(case_when(b_i_tend_to_avoid_things_h.factor == "Strongly Disagree" ~ 1,
                                                               b_i_tend_to_avoid_things_h.factor == "Somewhat Disagree" ~ 2,
                                                               b_i_tend_to_avoid_things_h.factor == "Neutral" ~ 3,
                                                               b_i_tend_to_avoid_things_h.factor == "Somewhat Agree" ~ 4,
                                                               b_i_tend_to_avoid_things_h.factor == "Strongly Agree" ~ 5)))

cherish <- cherish %>%  
         mutate(asking_qs_dich = ifelse(a_asking_questions_to_your.factor_numeric <= 3, 0, 1),
                understanding_dich = ifelse(c_understanding_medical_tr.factor_numeric <= 3, 0, 1),
                a_religion_dich = ifelse(a_religious_spiritual_beli.factor_numeric <= 3, 0, 1),
                b_religion_dich = ifelse(b_i_tend_to_avoid_things_h.factor_numeric <= 3, 0, 1),
           smoking_backwards = ifelse(q8.factor == 0, 1, 0),
         good_health_behaviors_cont = q6.factor + q7.factor + smoking_backwards,
         adverse_health_outcomes_cont = q10.factor + q12.factor + q14.factor,
         confidence_cont = a_asking_questions_to_your.factor_numeric + c_understanding_medical_tr.factor_numeric,
         confidence_avg = rowMeans(select(cherish, c(a_asking_questions_to_your.factor_numeric, c_understanding_medical_tr.factor_numeric))),
         religion_cont = a_religious_spiritual_beli.factor_numeric + b_i_tend_to_avoid_things_h.factor_numeric,
         religion_avg = rowMeans(select(cherish, c(a_religious_spiritual_beli.factor_numeric, b_i_tend_to_avoid_things_h.factor_numeric))),
         age_dich = ifelse(q28 <= 65, "<= 65", "> 65"),
         educ_dich = ifelse((q33.factor == "Grade 8 or less" |
                              q33.factor == "Some high school, no diploma" |
                               q33.factor == "High school graduate, GED or Equivalent"), "<= HS", ">= some college"),
         educ_dich_2 = ifelse((q33.factor == "Grade 8 or less" |
                              q33.factor == "Some high school, no diploma" |
                               q33.factor == "High school graduate, GED or Equivalent" |
                                q33.factor == "Some college, no degree"), "<= some college", ">= college degree"))
```

# Table 1
## Overall
```{r}
cherish %>% 
  select(q6.factor, q7.factor, q8.factor,
         q10.factor, q12.factor, q14.factor, 
         a_asking_questions_to_your.factor, c_understanding_medical_tr.factor,
         a_religious_spiritual_beli.factor, b_i_tend_to_avoid_things_h.factor,
         q28, q29.factor, q33.factor) %>% 
  tbl_summary(digits = ~ c(1)) %>% 
  bold_labels()
```

\newpage
## By first religious qst
```{r}
cherish %>% 
  select(q6.factor, q7.factor, q8.factor,
         q10.factor, q12.factor, q14.factor, 
         a_asking_questions_to_your.factor, c_understanding_medical_tr.factor,
         a_religious_spiritual_beli.factor, b_i_tend_to_avoid_things_h.factor,
         q28, q29.factor, q33.factor,
         a_religion_dich) %>% 
  tbl_summary(by = a_religion_dich,
              digits = ~ c(1)) %>% 
  bold_labels()
```

\newpage
## By second religious qst
```{r}
cherish %>% 
  select(q6.factor, q7.factor, q8.factor,
         q10.factor, q12.factor, q14.factor, 
         a_asking_questions_to_your.factor, c_understanding_medical_tr.factor,
         a_religious_spiritual_beli.factor, b_i_tend_to_avoid_things_h.factor,
         q28, q29.factor, q33.factor,
         b_religion_dich) %>% 
  tbl_summary(by = b_religion_dich,
              digits = ~ c(1)) %>% 
  bold_labels()
```

\newpage
# Individual outcomes regression
## Fruits and vegetables
```{r}
glm(q6.factor ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q6.factor ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q6.factor ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q6.factor ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## Physical activity
```{r}
glm(q7.factor ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q7.factor ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q7.factor ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q7.factor ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## Smoking
```{r}
glm(q8.factor ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q8.factor ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q8.factor ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q8.factor ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## Hypertension
```{r}
glm(q10.factor ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q10.factor ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q10.factor ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q10.factor ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## Cholesterol
```{r}
glm(q12.factor ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q12.factor ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q12.factor ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q12.factor ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## Diabetes
```{r}
glm(q14.factor ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q14.factor ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q14.factor ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(q14.factor ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## How confident are you in your ability to ask questions to your health providers?
```{r}
glm(asking_qs_dich ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(asking_qs_dich ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(asking_qs_dich ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(asking_qs_dich ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
## How confident are you in your ability to understand medical treatment plans?
```{r}
glm(understanding_dich ~ a_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(understanding_dich ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(understanding_dich ~ b_religion_dich,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)

glm(understanding_dich ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE)
```

\newpage
# Composite outcomes
## Health behaviors
```{r}
lm(good_health_behaviors_cont ~ a_religion_dich,
    data = cherish) %>% 
  tbl_regression()

lm(good_health_behaviors_cont ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish) %>% 
  tbl_regression()

lm(good_health_behaviors_cont ~ b_religion_dich,
    data = cherish) %>% 
  tbl_regression()

lm(good_health_behaviors_cont ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish) %>% 
  tbl_regression()
```

\newpage
## Adverse health outcomes
```{r}
lm(adverse_health_outcomes_cont ~ a_religion_dich,
    data = cherish) %>% 
  tbl_regression()

lm(adverse_health_outcomes_cont ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish) %>% 
  tbl_regression()

lm(adverse_health_outcomes_cont ~ b_religion_dich,
    data = cherish) %>% 
  tbl_regression()

lm(adverse_health_outcomes_cont ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish) %>% 
  tbl_regression()
```

\newpage
## Confidence in participating in medical care
```{r}
lm(confidence_cont ~ a_religion_dich,
    data = cherish) %>% 
  tbl_regression()

lm(confidence_cont ~ a_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish) %>% 
  tbl_regression()

lm(confidence_cont ~ b_religion_dich,
    data = cherish) %>% 
  tbl_regression()

lm(confidence_cont ~ b_religion_dich + age_dich + q29.factor + educ_dich_2,
    data = cherish) %>% 
  tbl_regression()
```